Carbon Renaissance Whitepaper 1.0

### 2021-07-24 carbon_renaissance/template.tex
update

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{doi}

@@

\begin{abstract}
We propose a Carbon offset design that creates natural economic incentives through business
processes tied to NFT tokens issued from enterprise to participating companies which connect
to Carbon offsetting processes. Upon audits of work, a fungible token (Green token) is issued to
companies involved based on a pre-negotiated ratio of tokens dispersed based on the quality of
the work and quality of the credit-worthiness of the companies involved. Green token supply
represents a collection and aggregation of all pollution prevention value that has happened thus
far.
\end{abstract}

@@

\section{Executive Summary}
\subsection{Mission and Vision}

We propose a Carbon offset design that creates natural economic incentives through business
processes tied to NFT tokens issued from enterprise to participating companies which connect
to Carbon offsetting processes. Upon audits of work, a fungible token (Green token) is issued to
companies involved based on a pre-negotiated ratio of tokens dispersed based on the quality of
the work and quality of the credit-worthiness of the companies involved. Green token supply
represents a collection and aggregation of all pollution prevention value that has happened thus
far.

@@

@@

There are a number of benefits that this Carbon offset model can provide.

@@

The CR process works in a cycle where the token can move to one of three different states over time (ie, statetokens). These states are: (a) Green; (b) Red; and (c) Black, and are usecase dependant. Green tokens (otherwise refereed as base tokens) are purchased on exchanges and represent the potential of what can be utilized for Carbon sequestration and are required to enter into the auditing process. Red tokens are non-tradable Non-Fungible Tokens (NFT) and represent unique IOU contracts between stakeholders who have intentions to sequester Carbon and those who offer the Carbon sequestration service; see Fig. \ref{fig:issue_redeem_green}. NFTs are unique digital assets that are stored on a blockchain and cannot be exchanged for one another, hence non-fungible. Finally, Black tokens represent sequestered Carbon. For instance, 100 Black tokens represent proof of 100 units of sequestered Carbon. These tokens are created when either Red or Green tokens are burned. Black tokens can be either held privately or can be publicly purchased on exchanges. Holding these tokens over time have the advantage of generating Green tokens which can generate additional revenue by being sold and recycled back into the system. We will be expounding further into the dynamics and utility behind these statetokens throughout this whitepaper.

\subsubsection{NFT Tokens}

NFT tokens represent legal contracts and partnership with NFT issuances. They have the ability to white and black list those issuances to control the conversions and have the authority to issue monetary redemptions of those NFT’s if they are breaking contract rules. Bundling these NFTs into these promissory contracts helps decouple concerns between pollution prevention companies and users of the credits. This idea allows stakeholders to seamlessly enable onboarding of partners without upfront costs. This disruptive technology allows for the seamless onboarding of partners without upfront costs and regulatory pressures that would otherwise slow down the workflow process using traditional means. Not requiring upfront investment and low barrier of entry for existing pollution prevention services will greatly increase the chance of network effects. Participants can target businesses by offering them the NFT and liquidity on the open market in exchange for their services.

@@

@@

Using our carbon offset token program way, governments can purchase carbon offsets
which are an efficient spend of budget against environmental impacts of its economy and
reduce taxes to those that inhibit green spending habits such as buying local and not going
over their carbon footprint quota per person. A positive reinforcement model will always be
unanimously acceptable to both the wealthy and the poor. Creating a positive feedback loop
to incentivize people to adapt their spending habits is a great way to find new efficiencies
and invent “greener” technologies due to the higher demand for such technologies and
services. The work here will be to assign carbon scores to goods and services and also
assign spending against carbon ratings of goods and services. People that have a negative
carbon footprint can be paid in Green tokens creating a powerful driver to reduce pollution
and assigning monetary benefits which can be part of a UBI system, one which is tied to
actual production and verified work.

@@

@@

The NFT stays in the possession of the sequesterer until the work has been performed and verified via the auditing process. Once complete, the NFT is burned and exchanged for both Black tokens as proof of sequestration and Green tokens which can be sold for revenue. Further to that, Black tokens can be held by sequesterer which when held over time slowly burn back into Green tokens. Each NFT may have its
own rules, regulations and even sequestering costs factoring in base asset to NFT cost ratios.

@@

@@

\begin{figure}
\centering
\includegraphics[width=4in]{state_diagram.png}
\caption{State transition diagram for Markov chain token model illustrating the probability of a token transitioning between states (ie, Green, NFT, and Burned) over a unit of time.} 
\label{fig:state_diagram}
\end{figure}

\subsection{Benefits}

\begin{itemize}
\item Creates an analogous “miner” network, localized to jurisdiction or to company. Tap into
the work of others by infiltrating different geographic and types of sequestering for you,
even letting others race to acquire better sequestering techniques (like how bitcoin
miners raced to create asics). The more sequestoring they can do the more profits they
achieve.
\item Creates an inflation/deflation environment for Basecoin for a healthy market which is
realistic. One way deflationary markets suffer from utility concerns (first come first serve
won’t work here) and inflationary markets have little demand. One monetary instrument
for the entire system that simplifies economics and buy-in from government/enterprises
\item Allows separation of concerns between sequestoring companies and users of the
credits
\item Enabled onboarding of partners without upfront costs. Allows you as a company
facilitating the NFT to Basecoin conversions to issue new NFT’s strategically to
countries, businesses etc without requiring an upfront investment from those companies
(you can hold a deposit externally to avoid deadbeat companies that do not follow
through). Not requiring upfront investment and low barrier of entry for existing
sequestorers will greatly increase the chance of network effects. You can target any
business doing something like this and offer them the NFT and liquidity on the open
market in exchange for their services
\item Legal contracts and partnership with NFT issuances with ability to white/black list those
issuances to control the conversions and thus monetary redemptions of those NFT’s if
they are breaking contract rules
\item There is no responsiveness required on the sequestorers part. They can do as little or as
much work as they want, no queues needed and no required customer acquisitions. For
any work they do they should be paid (as long as it's audited and verified). The more
efficient their work becomes the more they can sequester and thus more they get paid.
The act of decoupling sequestoring from customer demand, makes the whole system
more efficient and greener
\item Works with any type of sequestoring model, each NFT can be uniquely identified in
terms of costs of base coin to NFT valuations based on the capture models storage vs
utility vs other
\item In order to mint new NFT’s, Basecoin supply increases but not the available supply (as
the NFT is not tradeable only the base coin is and thus the market cap of the base coin rises on issuances. The available supply increases when an NFT is burned in exchange
for Basecoin
\item Pre-negotiated rates (even in non-token values if needed) are possible between
partners/sequestorers and CR for NFT to Basecoin exchange. This will give ability to
offload speculative concerns on the sequestorer's part to CR, however CR can also raise
capital to offer liquidity on the markets as needed as well.
\end{itemize}

\subsection{Revenue Models}

\begin{itemize}
\item Percentage of profits on the NFT to Basecoin conversions for recurring revenue as a
platform as a service
\item CR sequestoring and earning Basecoin. Hold or sell
\item Value added services on top, softwares, wallets and other things some
companies/partners may pay extra for.
\end{itemize}

@@

It was requested that we create a fungible token for the purpose of share allocations in a
company represented as a token product on blockchain. Also these shares should not be
transferable unless explicitly allowed by CR. We can enable this functionality on Syscoin
through Notary services which will allow a case by case basis for transaction authorization
between P2P transfers. See spec:
https://github.com/syscoin/sips/blob/master/sip-0002.mediawiki

We should define the Maximum supply and precision as well as token symbol.
Token to sell to raise funds:
\begin{itemize}
\item Max supply: 100m
\item Precision: 8
\item Total raise: sell 10m upfront @ \$10
\item Token symbol: GCX
\end{itemize}

Token to issue as NFT for companies
\begin{itemize}
\item Max supply: MAX
\item Precision: 8
\item Token symbol: CX
\end{itemize}

Individual NFT:
\begin{itemize}
\item Precision: 8
\item Max supply: MAX
\end{itemize}

@@

\begin{equation}
P_{\mu} = 
\begin{bmatrix}
0.95 & 0  & 0.05 \\
0.05 & 0.9  & 0.05 \\
0.01 & 0 & 0.99
\end{bmatrix}
\label{e:transition_matrix}
\end{equation}
where the frequency is monthly, and the states are represented as green, NFT, burned respectively. In Fig \ref{fig:gas}, we represent this Markov process as a directed graph with edges labelled by the transition probabilities in (\ref{e:transition_matrix}).

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c c|c|c|c| } 
\hline
 & \multicolumn{4}{ c |}{ Next State } \\
 &  & Green & NFT & Burned \\
\hline
\multirow{ 3}{*}{Current State} & Green & $P(X_{n+1} = g | X_{n} = g )$ & $P(X_{n+1} = r | X_{n} = g )$ & $P(X_{n+1} = b | X_{n} = g )$ \\
& NFT & $P(X_{n+1} = g | X_{n} = r )$ & $P(X_{n+1} = r | X_{n} = r )$ & $P(X_{n+1} = b | X_{n} = r )$ \\
& Burned & $P(X_{n+1} = g | X_{n} = b )$ & $P(X_{n+1} = r | X_{n} = b )$ & $P(X_{n+1} = b | X_{n} = b )$ \\
\hline
\end{tabular}
\caption{Transition state matrix for token model detailing probabilities of transitioning from current to next state over a unit of time. The token states are denoted by Green $\rightarrow$ g, NFT $\rightarrow$ r, and Burred $\rightarrow$ b.}
\label{table:pow_vs_pos}
\end{table}

\begin{figure}
\centering
\includegraphics[width=4in]{issue_redeem_green.png}
\caption{xxx} 
\label{fig:issue_redeem_green}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=4in]{red_green.png}
\caption{xxx} 
\label{fig:red_green}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=4in]{green_black.png}
\caption{xxx} 
\label{fig:green_black}
\end{figure}

@@

@@

\begin{table}[h]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 Year & median & lwr 5\% & upr 5\% \\
\hline
1 & 4,730,000 & 3,080,000 & 6,230,000 \\
2 & 7,960,000 & 7,040,000 & 9,690,000 \\
3 & 11,000,000 & 9,800,000 & 12,260,000 \\
4 & 13,620,000 & 12,100,000 & 14,770,000  \\
5 & 16,060,000 & 15,120,000 & 19,710,000 \\
\hline
\end{tabular}
\caption{Simulated number of sequestered tons of Carbon assuming transition matrix (\ref{e:transition_matrix}) as business targets}
\label{table:pow_vs_pos}
\end{table}

\subsection{Token Architecture}

\section{Open Issues}

\subsection{Jurisdictional Requirements}

\begin{itemize}
\item What if companies need jurisdictional guarantees on sequestration to fulfill local
government driven quota’s.
\begin{itemize}
\item Companies can buy directly from a local sequestration provider, and buy their
NFT’s for a premium (to jump in front of a queue) and convert into Basecoin from
CR (pay requisite small fees for doing so) and then burn tokens through standard
means as discussed in the proposal. The deals would be directly with NFT
partners and sequestration companies and so are localized based on company
jurisdiction.
\item Companies alternatively can buy directly from CR to jump ahead of the audit trail
(aforementioned queue), which will put more demand on those jurisdictions to
produce more sequestration. This would be an option if enough sequestration is
available for example.
\item The premiums paid for these higher demands are not factored into the Basecoin
market unless the drivers of these markets push up price naturally as global
aggregate prices go up based on these drivers if they are big enough.
\end{itemize}
\item There would be a timestamped sequestration audit trail that goes on the blockchain and
accessible publicly (through hyperlink in the asset public data field). This would be a live
document that would update with signatures of auditors registered with Digital Identities
and timestamps of where/when they happened.
\item If companies require localized sequestration in exchange for burning Basecoin then
upon burn when the time stamped audit trail is updated to reflect “consumed”
sequestrations CR can simply pick and choose which sequestration’s to qualify for that
particular carbon credit application. Ie: if MSFT needs 100 tons American sequestration
only, and we have 100 tons of American sequestration in the audit trail, we can choose those sequestrations and label them as consumed. Future American sequestration
requests either need to pay the American sequestors or wait for more sequestrations to
register from American sequestors. Under normal circumstances the audit trail can be
consumed chronologically.
\item It would be ideal to have this a global thing under l'accord de Paris so that there are no
jurisdictional requirements because otherwise there is incentive to strike side-deals with
companies directly, if the sequestration is fungible it makes for more clear and
understandable usage of the system and a more stable supply/demand curve of Basecoin. It
is almost like the Euro currency, where multiple countries each with their own policies use a
single currency, it is not a total failure but better to have one policy that is applicable to avoid
chances of corruption. However it may not be up to us, and so we can employ this strategy
based on market research if required.
\item The timestamped log will bring about transparency between consumed sequestrations, the
actual registered audited sequestrations and allow one to audit that the supply of Basecoin’s
accurately represents the audited sequestration amounts since 1 Basecoin can represent a
certain amount of sequestration (per ton?). It will allow companies to know what is available
for consumption should there be requirements around jurisdictional consumption.
\end{itemize}

@@

\subsection{Speculative vs Stable}

Proposed design is a mix of speculative for companies requiring credits (Basecoin) and Stable
(can set rates and offload speculative risks for companies dealing with sequestoring). While at
the same time allowing for parallelization of sequestoring for faster more responsive supply side
mechanics of Basecoin (carbon credits).

\begin{itemize}
\item 1 ton of carbon assigned amount of tokens (based on cost in \$)
\item Start 1 for 1 but over time as tokens become burned the ratio will change, 1 ton of
carbon will be less than 1 token
\item This model adds speculation and thus enterprises may buy and hoard tokens to reduce
their own costs over time and also for potential gains. The cost in \$ should remain
consistent however as the ratio drops on how many tokens required for 1 ton of carbon
emissions.
\item Is deflationary only and so has a supply/demand equilibrium problem
\end{itemize}

\subsubsection{Speculative}

\begin{itemize}
\item 1:1 ratio constant
\item Need to mint new tokens according to how many tons exist in the world, if amount being
sequestered globally is > than new pollution then tokens become deflationary, otherwise
it's inflationary
\item Can pollution be determined through census information that is dependable enough?
\item Over time the goal is for pollution to drop and thus supply to reduce. As the pollution
drops the cost per carbon to cleanup reduces?
\item So this removes speculation play on the token to make it friendly for enterprises to use
and buy only as required (not have to purchase in advance due to speculation
concerns).
\item This model assumes all global carbon credits are modelled in the supply/demand market
of the token. If global pollution is not modelled it is not 1:1 at scale.
\end{itemize}

@@

Bitcoin miners themselves are under alot of pressure for polluting the environment to secure the
Bitcoin network. They can use such a system which is actually using Bitcoin’s PoW indirectly to
secure such a system but decreasing their carbon footprint. This may be something that miners
would be interested in consuming driving adoption and awareness.

Creating a standards body to work with stakefish/f2pool and other miners to find a way to
specify how carbon offsets can be applied to the industry effectively. How can “green”
tokenization work with existing market initiatives related to NFT and maybe even FT tokens?

Better understand AMM model pertaining to a more distributed system where sequestorers can
be direct to market. Understand the need for differing markets based on quality metrics.

Green purchase, burn to goto Red where there is a Queue in response to physical sequestoring
and Black once sequestering happens and Red is burned. In this model there is a direct relation
between purchase of green and sequestering. Is this a requirement? In the proposed design we
establish a more frictionless system but do not assume that there is a direct relation between
green Basecoin and sequestering (It is indirectly related through the network of sequestorers
that get paid Basecoin to do work). A queue system inherently decreases efficiency
exponentially to the number of parallel sequestorers as there needs to be coordination, and
delays as well as mapping of which sequestering is for who adds complexity overall.

\section{Research To-dos}

\begin{itemize}
\item \$10 per token to 1 ton of Carbon: needs research to determine costs
\item Carbon sequestration is subjective and no trust-less  as whole thing can be corrupted by few auditors
\begin{itemize}
\item need to think about concessions to be put in place to thwart these potential bad actors
\end{itemize}
\item Carbon sequestration work/costs is akin to electricity costs and different jurisdictions will have different sequestration costs
\end{itemize}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}		% Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{doi}
\usepackage{gensymb}

@@

\begin{abstract}

We introduce a Carbon offsetting program through the tokenization of work done (ie, via Green tokens) on a blockchain. We utilize Non-fungible tokens as IOU contracts to facilitate engagement between stakeholders interested in pollution prevention and those performing the Carbon offsetting. To incentivize adoption, a Black reward token is offered for those who utilize the system, which can be staked to acquire  Green tokens introduced to the supply

\end{abstract}

@@

\section{Executive Summary}

\subsection{Mission and Vision}

We propose a Carbon offset design that creates natural economic incentives through business
processes tied to NFT tokens issued from enterprise to participating companies which connect
to Carbon offsetting processes. Upon audits of work, a fungible token (Green token) is issued to
companies involved based on a pre-negotiated ratio of tokens dispersed based on the quality of
the work and quality of the credit-worthiness of the companies involved. Green tokens
represents auditing work done for carbon offsetting.

@@

\subsection{Background}

Climate change is a defined as global warming stemming from greenhouse gas emissions resulting from major shifts in weather patterns. As a result, this issue has recently garnered much attention on the world stage. According to \cite{Glo21}, it is estimated that human activity accounts for 1.0 $^\circ$C of global warming above pre-industrial levels, and estimate that global warming is likely to reach 1.5$^\circ$C between 2030 and 2052. The Edgar time series set shows that since the beginning of the 21$^{st}$ \cite{EDGAR19}, fossil CO$_{2}$ emissions have increased compared to the three previous decades; see Fig \ref{fig:edgars_co2_emissions}. It also shows that, as of 2018, global fossil CO$_{2}$ emissions have reached a total of \# Gt CO$_{2}$. However, according to \cite{Liu20}, emissions have fallen \~ 1,900 MtCO$_{2}$ from 2019 to 2020 mainly in the aviation and shipping sector due to the slowing of economic activity stemming from the 2020 pandemic. To combat this, carbon offsetting is the process by which many players are handling this issue.

\begin{figure}[h]
\centering
\includegraphics[width=5in]{edgars_co2_emissions.png}
\caption{Global Greenhouse Gas (GHG) emission per sector; see \cite{EDGAR19}. We can see the Power industry account for a large portion of global emissions, which provides insight as to where the largest opportunity for carbon reduction is found.} 
\label{fig:edgars_co2_emissions}
\end{figure}

Carbon offsetting is done via sequestration which is the process where atmospheric carbon dioxide is captured and stored for the purpose of abating climate change. After carbon is captured, it goes mainly one of two ways \cite{CBC19}: (a) permanently stored underground; or (b) converted into a carbon-containing product. Currently, the market for corporate procurement for carbon removal is very undeveloped. However, there are currently a number of organizations that have made strides to address this issue; which include Amazon, Apple, BCG, Delta, Facebook, Google, Mars, Shopify, Stripe, Swiss Re, United and Velux \cite{Mic21}. Of the aforementioned, Shopify, Stripe and Microsoft are making carbon removal a core focus in their business. More specifically Microsoft has a plan to remove carbon that they emit, and came to key conclusions. Namely, they can not meet current carbon negative commitments and estimate that they need to remove 6 Million Tons of carbon in 2030. Hence, an RFP was sent out in 2020 and 79 applications were received and 15 organizations were selected representing 1.3 Million metric tons of carbon removal. Their project selection process was based on several criteria: (a) Global carbon removal potential; (b) Affordability targeting \$15 per mtCO$_{2}$; (c) climate equity; (d) technology innovation; and (e) other sustainability dimensions.

In 2019, the National Academies of Sciences, Engineering, and Medicine investigated the likely market size for Negative Emissions Technologies (NET) \cite{NET19}, where they discuss how much Carbon uptake is needed to meet Paris Agreement goals. They estimate that \~ 10 GtCO$_{2}$ / yr is required globally by midcentury and \~ 20 GtCO$_{2}$ / yr globally by centuries end to meet these goals. Six key sequestration technologies are identified which are: (a) Coastal carbon blue; (b) Terrestrial carbon removal and sequestration; (c) Bioenergy with carbon capture and sequestration (BECCS); (d) Geological sequestration; (e) Direct air capture;  and (f) Carbon mineralization. Of these aforementioned technologies, the former four are ready for large-scale deployment; see Table \ref{table:net} for estimated potential rates across US and the Globe.

\begin{table}[h]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 Negative Emission Technology & Estimated Cost (\$/tCo$_{2}$) &\multicolumn{2}{ c |}{ Upper Bound for Safe Potential rate of CO$_{2}$ (GtCO$_{2}$/y)}  \\
  & & US & Global \\
\hline
Coastal blue carbon & L & 0.02 & 0.13  \\
Afforestation / Reforestation & L & 0.15 & 1  \\
Forest management & L & 0.1 & 1.5  \\
Agricultural soils & L to M & 0.25 & 3  \\
BECCS & M & 0.5 & 3.5-5.2  \\
Direct air capture & H & 0 & 0  \\
Carbon mineralization & M to H & unknown & unknown \\
Total &  & 1.02 & 9.13-10.83 \\
\hline
\end{tabular}
\caption{Estimated potential rates of CO$_{2}$ removal for various Negative Emission Technologies (measured in GtCO$_{2}$ / y) for the US and across the globe; see \cite{NET19}, we see BECCS offer the best opportunity.}
\label{table:net}
\end{table}

@@

@@

The CR process works in a cycle where the token can move to one of three different states over time (ie, statetokens). These states are: (a) Green; (b) Red; and (c) Black, and are usecase dependant. Green tokens (otherwise refereed as base tokens) are purchased on exchanges and represent the potential of what can be utilized for Carbon sequestration and are required to enter into the auditing process. Red tokens are non-tradable Non-Fungible Tokens (NFT) and represent unique IOU contracts between stakeholders who have intentions to sequester Carbon and those who offer the Carbon sequestration service; see Fig. \ref{fig:red_to_green}. NFTs are unique digital assets that are stored on a blockchain and cannot be exchanged for one another, hence non-fungible. Finally, Black tokens represent sequestered Carbon. For instance, 100 Black tokens represent proof of 100 units of sequestered Carbon. These tokens are created when either Red or Green tokens are burned. Black tokens can be either held privately or can be publicly purchased on exchanges. Holding these tokens over time have the advantage of generating Green tokens which can generate additional revenue by being sold and recycled back into the system. We will be expounding further into the dynamics and utility behind these statetokens throughout this whitepaper.

\subsubsection{NFT Tokens}
\label{section:nft_tokens}

NFT tokens represent legal contracts and partnership with NFT issuances, see Fig \ref{fig:red_green_issue}. They have the ability to white and black list those issuances to control the conversions and have the authority to issue monetary redemptions of those NFT’s if they are breaking contract rules. Bundling these NFTs into these promissory contracts helps decouple concerns between pollution prevention companies and users of the credits. This idea allows stakeholders to seamlessly enable onboarding of partners without upfront costs. This disruptive technology allows for the seamless onboarding of partners without upfront costs and regulatory pressures that would otherwise slow down the workflow process using traditional means. Not requiring upfront investment and low barrier of entry for existing pollution prevention services will greatly increase the chance of network effects. Participants can target businesses by offering them the NFT and liquidity on the open market in exchange for their services.

@@

\begin{figure}[h]
\centering
\includegraphics[width=4in]{red_green_issue.png}
\caption{Flow of NFT issuances and redemptions between pollution prevention stakeholders and sequesterors, which is all managed by CR and marks stakeholder relationship when burning Red tokens in exchange for Green} 
\label{fig:red_green_issue}
\end{figure}

@@

Using our carbon offset token program way, governments can purchase carbon offsets
which are an efficient spend of budget against environmental impacts of its economy and
reduce taxes to those that inhibit green spending habits such as buying local and not going
over their carbon footprint quota per person. A positive reinforcement model will always be
unanimously acceptable to both the wealthy and the poor. Creating a positive feedback loop
to incentivize people to adapt their spending habits is a great way to find new efficiencies
and invent \emph{greener} technologies due to the higher demand for such technologies and
services. The work here will be to assign carbon scores to goods and services and also
assign spending against carbon ratings of goods and services. People that have a negative
carbon footprint can be paid in Green tokens creating a powerful driver to reduce pollution
and assigning monetary benefits which can be part of a UBI system, one which is tied to
actual production and verified work.

@@

\begin{figure}[h]
\centering
\includegraphics[width=4in]{state_diagram.png}
\caption{State transition diagram for Markov chain token model illustrating the probability of a token transitioning between states (ie, Green, NFT, and Burned) over a unit of time.} 
\label{fig:state_diagram}
\end{figure}

@@

The NFT stays in the possession of the sequesterer until the work has been performed and verified via the auditing process, see Fig \ref{fig:red_to_green}. Once complete, the NFT is burned and exchanged for both Black tokens as proof of sequestration and Green tokens which can be sold for revenue. Further to that, Black tokens can be held by sequesterer which when held over time slowly burn back into Green tokens. Each NFT may have its
own rules, regulations and even sequestering costs factoring in base asset to NFT cost ratios.

\begin{figure}[h]
\centering
\includegraphics[width=4in]{red_to_green.png}
\caption{ Process workflow illustrating how Green tokens are minted through the auditing of Red NFT contracts } 
\label{fig:red_to_green}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=4in]{green_to_black.png}
\caption{ Process workflow illustrating how Green tokens are burned to mint Black tokens } 
\label{fig:green_to_black}
\end{figure}

@@

@@

It was requested that we create a fungible token for the purpose of share allocations in a company represented as a token product on blockchain. Also, these shares should not be transferable unless explicitly allowed by CR. We can enable this functionality on Syscoin through Notary services which will allow a case-by-case basis for transaction authorization between P2P transfers. Here are the following token specifications:

Token to sell to raise funds
\begin{itemize}
\item \textbf{Max supply}: 100m
\item \textbf{Precision}: 8
\item \textbf{Total raise}: sell 10m upfront @ \$10
\item \textbf{Token symbol}: GCX
\end{itemize}

Token to issue as NFT for companies
\begin{itemize}
\item \textbf{Max supply}: MAX
\item \textbf{Precision}: 8
\item \textbf{Token symbol}: CX
\end{itemize}

Token received from burning GCX or CX
\begin{itemize}
\item \textbf{Max supply}: MAX
\item \textbf{Precision}: 8
\item \textbf{Token symbol}: BCX
\end{itemize}

Individual NFT:
\begin{itemize}
\item \textbf{Precision}: 8
\item \textbf{Max supply}: MAX
\end{itemize}

@@

\begin{equation}
P_{\mu} = 
\begin{bmatrix}
0.95 & 0  & 0.05 \\
0.05 & 0.9  & 0.05 \\
0.01 & 0 & 0.99
\end{bmatrix}
\label{e:transition_matrix}
\end{equation}
where the frequency is monthly, and the states are represented as green, NFT, burned respectively. In Fig \ref{fig:state_diagram}, we represent this Markov process as a directed graph with edges labelled by the transition probabilities in (\ref{e:transition_matrix}).

@@

\begin{table}[h!]
\centering
\begin{tabular}{|c c|c|c|c| } 
\hline
 & \multicolumn{4}{ c |}{ Next State } \\
 &  & Green & NFT & Burned \\
\hline
\multirow{ 3}{*}{Current State} & Green & $P(X_{n+1} = g | X_{n} = g )$ & $P(X_{n+1} = r | X_{n} = g )$ & $P(X_{n+1} = b | X_{n} = g )$ \\
& NFT & $P(X_{n+1} = g | X_{n} = r )$ & $P(X_{n+1} = r | X_{n} = r )$ & $P(X_{n+1} = b | X_{n} = r )$ \\
& Burned & $P(X_{n+1} = g | X_{n} = b )$ & $P(X_{n+1} = r | X_{n} = b )$ & $P(X_{n+1} = b | X_{n} = b )$ \\
\hline
\end{tabular}
\caption{Transition state matrix for token model detailing probabilities of transitioning from current to next state over a unit of time. The token states are denoted by Green $\rightarrow$ g, NFT $\rightarrow$ r, and Burred $\rightarrow$ b.}
\label{table:trans_state_matrix}
\end{table}

@@

\begin{figure}
\centering
\includegraphics[width=4in]{burned_tokens.png}
\caption{Plot of simulated number of sequestered tons of Carbon } 
\label{fig:burned_tokens}
\end{figure}

@@

Both Green and Black tokens are fungible hence tradable on exchanges, but serve different ways to generate revenue. Green tokens are earned from sequestoring Carbon (through NFT to Green token conversions) which can be sold for profit. Black tokens are earned through burning NFT or Green tokens. These Black tokens can be held privately which burn slowly over time (at a pre-determined rate) producing Green tokens that can sold for profit or reintegrated into the system. Aside from the tokens themselves, value added services such as softwares, wallets that companies may pay services for.

\begin{table}[h]
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 Year & median & lwr 5\% & upr 95\% \\
\hline
1 & 4,730,000 & 3,080,000 & 6,230,000 \\
2 & 7,960,000 & 7,040,000 & 9,690,000 \\
3 & 11,000,000 & 9,800,000 & 12,260,000 \\
4 & 13,620,000 & 12,100,000 & 14,770,000  \\
5 & 16,060,000 & 15,120,000 & 19,710,000 \\
\hline
\end{tabular}
\caption{Simulated number of sequestered tons of Carbon assuming transition matrix (\ref{e:transition_matrix}) as business targets}
\label{table:pow_vs_pos}
\end{table}

\section{Management on Jurisdictional Level}

From time to time, companies may need cooperation with local governments who have requirements to fulfill quotas for its jurisdiction, which can be managed using a number of strategies. First, companies can buy directly from a local sequestration provider, and buy their NFT’s for a premium (ie, move to front of queue) which can been converted to Green tokens from CR (ie, pay requisite small fees for doing so). Upon fulfilling the needs of the NFT contract, tokens are then burned as described in Section \ref{section:nft_tokens}. Contracts would be directly with NFT partners and sequestration companies, hence localized based on jurisdiction. Alternatively, companies can skip the auditing process and buy directly from CR via the aforementioned queue. Doing this puts more demand on those jurisdictions to produce more sequestration and would be an option if enough sequestration is available. Finally, premiums paid for these higher demands are not factored into the Green token market unless larger market players drive prices upwards as global aggregate prices go up.

Evidence of the sequestration audit trail would need to be timestamped and recorded on the blockchain, which would be publicly accessible through hyperlink in the asset public data field. This would be a live document that would update with signatures of auditors registered with Digital Identities and along with any associated metadata. The timestamped log will bring about transparency between consumed sequestrations, the actual registered audited sequestrations and allow one to audit that the supply of Basecoin’s accurately represents the audited sequestration amounts since 1 Basecoin can represent a certain amount of Carbon sequestration tonnage. It will allow companies to know what is available for consumption should there be requirements around jurisdictional consumption.

If companies require localized sequestration in exchange for burning Green tokens, then CR can select which sequestration’s to qualify for that particular carbon credit application. Upon completion, tokens are burned and the time stamped audit trail is updated to reflect \emph{consumed} sequestrations. For instance, say MSFT requires 100 tons of American sequestration, and we have 100 tons of American sequestration in the audit trail, we can then choose those sequestrations and label them as consumed. Future American sequestration requests either need to pay the American sequestors, or wait for more sequestrations to register from American sequestors. However, under normal circumstances, the audit trail can be processed sequentially.

It would be ideal to manage such an effort at the global level (eg, under L'Accord de Paris) so that there are no jurisdictional requirements. Otherwise, the incentive would be to negotiate with companies directly; if the sequestration is fungible, the system can be more effectively managed through better stable supply and demand dynamics. For instance, this can be analogous to the Euro currency, where multiple countries, each with their own policies, utilize a single currency. This may be less ideal, but a having this managed under a single policy may help avoid chances of corruption. However, we may not have control over this, and so we can employ this strategy upon further investigation, if need be.

@@

\subsection{Sequestration Costs}

\begin{itemize}
\item A Marginal Abatement Cost Curve (MAC curve or MACC) is a succinct and straightforward tool for presenting carbon emissions abatement options relative to a baseline (typically a business-as-usual pathway); \cite{Mck09}
\item Fossil fuel power plants with carbon capture and storage cost an estimated $43 to $95 US per tonne, a 2018 study by Harvard and Yale researchers found; \cite{Gil18}
\item 
\end{itemize}

\subsection{Carbon Exchange Rate: Speculative vs Stable}

Regarding the Green token to Carbon exchange rate, we adopt a hybrid model. That is offering both a fixed and floating speculative rate to users of the system. This is done by allowing a floating speculative rate for companies requiring credits (ie, Green Tokens), while at the same time allowing for the setting of stable rates through the offloading of speculative risks for companies dealing with sequestering. Doing this allows for more responsive supply side mechanics of Green tokens (ie, carbon credits).

Regarding the stable component we keep the ratio as a constant 1:1; that is one Green token for one one ton of sequestered Carbon. Doing this removes the need for governments and large enterprises to have to make speculative purchases, hence make the system more usable. The number of new minted tokens depends on the number of new tons of carbon that are being introduced into the atmosphere. If the amount of new Carbon being sequestered globally is greater than new pollution then Green tokens become deflationary, otherwise it's inflationary.

Alternatively, regarding the speculative component, we begin the process with a 1:1 ratio, however the ratio changes as tokens are burned over time. Hence, making one ton of carbon to be less than one Green token. This model adds speculation enticing enterprises to purchase and remove tokens from the supply which reduce costs over time and also for potential gains. While the dollars cost value remains consistent, the number of tokens required for one ton of carbon emissions drops. Hence putting deflationary pressures on the supply.

@@

In this whitepaper we propose a Carbon offset design program using blockchain Tokenization. The advantages to using such technology are: (a) minimizes red tape allowing for improved accessibility; (b) improves efficiency by allowing for direct peer-to-peer transactions eliminating third part involvement; (c) provides transparency and trust on an immutable public ledger database; (d) provides global access across various jurisdictions; and (e) drives new payment innovations that go beyond the limitations of current fiat money system. Our proposal is comprised of three tokens (Green, Red, and Black tokens); the action of transitioning from one token state to another is called burning. Green tokens are required to enter into the Carbon offsetting process directly and are awarded as work done via the auditing process. Next, NFT tokens serve as IOU contracts to sequester Carbon. Finally, Black tokens serve as proof of burn which can be staked to gain more Green tokens as incentives.

\section{To-dos: Research, Analysis and Presentation}
